---
title: "InteroMentalHealth"
output: html_document
date: '2022-06-21'
---

# Load packages 
```{r}
# clean slate to be sure
rm(list = ls())

# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(tidyverse, here, corrplot, ggcorrplot, heatmap3, patchwork, cowplot, ggpubr, R.matlab, dplyr, BayesFactor,RColorBrewer, psych, ppcor, reshape2) 
 
```


# Read merged data of intero & mental health (& preprocess intero)
```{r}
alldata <- read_csv(here::here("data", "alldata_acc.csv"))
#colSums(!is.na(alldata)) # - 513 HRDT, 267 RRST

# preprocess slope & M-Ratio for intero tasks

# Invert scale of hrd/extero slope (so higher = steeper slope (same as RRST)) (for both intero & extero)
alldata[ ,'HRD_slope'] <- -(alldata[ ,'HRD_slope'])
alldata[ ,'HRDextero_slope'] <- -(alldata[ ,'HRDextero_slope'])


# M-Ratio: Replace negative M-Ratio values with NA 
cols_to_modify <- c("mratio_hrd", "mratio_rrst", "mratio_extero")
alldata[cols_to_modify] <- lapply(alldata[cols_to_modify], function(x) ifelse(x < 0, NA, x))

# M-Ratio: remove high outliers from M-Ratio (MAD-based outlier removal to selected columns) 
alldata[cols_to_modify] <- lapply(alldata[cols_to_modify], function(x) {
  median_x <- median(x, na.rm = TRUE)
  mad_x <- mad(x, na.rm = TRUE)
  x[abs(x - median_x) > 3 * mad_x] <- NA
  return(x) 
})

```


# plot data & save descriptive tables
```{r}
colnames(alldata) <- gsub("_", ".", colnames(alldata)) # change _ to . in colnames
cols = c("RRST.conf", "RRST.slope", "RRST.thresh", "mratio.rrst", "HRD.conf", "HRD.slope", "HRD.thresh", "HRD.absthresh", "mratio.hrd", "HRDextero.conf", "HRDextero.slope", "HRDextero.thresh", "HRDextero.absthresh", "mratio.extero", "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD",  "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity", 'aq10', 'asrs.a.sum', 'asrs.b.sum', "cfq.sum", "covid", "cusados", "dq5", "facit.sum", 'iri.FS', 'iri.EC', 'iri.PT', 'iri.PD', 'isi', "maas", 'maia.notice', 'maia.ndistract', 'maia.nworry', 'maia.attnReg', 'maia.EmoAware', 'maia.SelfRef', 'maia.listen', 'maia.trust', 'mdi', 'mdq.pt1.sum.of.yes', 'mfi.physical.fatigue', 'mfi.general.fatigue', 'mfi.reduced.activity', 'mfi.reduced.motivation', 'mfi.mental.fatigue', 'mpsss.so', 'mpsss.fam', 'mpsss.friends', "oci.r", "pas", "pcl", 'phq9', 'phq15', "psqi.sum", 'pss', "sbsds", 'sias', "speq.p", "speq.c", "speq.cog", "speq.m", "speq.teps", "stai.state" , 'stai.trait', "sticsa.gm.cog", "sticsa.gm.som", 'wemwbs', 'who', 'whoqol.quality.life', 'whoqol.physical', 'whoqol.phychological', 'whoqol.social.relationships', 'whoqol.enviroment')
corrdata <- alldata[ ,cols]
# Loop through each column in the data frame
for (colname in names(corrdata)) {
  # Create a histogram for the current column
  hist(corrdata[[colname]], main = colname, xlab = colname, col = 'lightblue', border = 'black')
}

```


# Correlation matrix & scatterplot functions
```{r}

cormatrix_full <- function(cordata, title, subtitle, savepath) {
  pval_fdr <- psych::corr.test(cordata, method = "spearman", adjust = "fdr")$p 
  rval_fdr <- psych::corr.test(cordata, method = "spearman", adjust = "fdr")$r

  cp1 <- ggcorrplot(rval_fdr,  hc.order=FALSE, p.mat = pval_fdr,
             type='full',  method = "square", insig='blank', sig.level = 0.05,  
             outline.col = "black",
             #lab = TRUE,  # Add correlation values
             #lab_col = "black",               # Label color
             #lab_size = 1.5,                    # Label size
             #digits = 2, # 2 decimal points
             ggtheme = ggplot2::theme_minimal,
             tl.cex = 8,
            colors = c("#4a6fe3", "white", "#d33f6a")) + 
    ggtitle(title) +
    labs(subtitle = subtitle)+
    theme(
      axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1),
      axis.text.y = ggtext::element_markdown()
    )
  
  png(filename = savepath, res = 300, units = "cm", width = 15, height = 15) 
  print(cp1)
  dev.off()
}


cormatrix_selected <- function(cordata, xlabel, ylabel, xnum, ynum, savepath) {
  # Correlation plots
  cormatrix <- t(psych::corr.test(cordata, method = "spearman", adjust = "fdr")$r[1:xnum, (xnum+1):(xnum+ynum)]) 
  cor_pvals <- t(psych::corr.test(cordata, method = "spearman", adjust = "fdr")$p[1:xnum, (xnum+1):(xnum+ynum)])
  png(filename = savepath, res = 300, height = ((ynum*3)+2), width = ((xnum*3)+2), units = "cm") # width for factors
  # Plot the correlation matrix with significance markers
  corrplot::corrplot(cormatrix,
                     method = "color",
                     addCoef.col = 'black',
                     cl.pos = 'n',
                     col.lim = c(min(cormatrix), max(cormatrix)),
                     tl.col = "black",
                     col = colorRampPalette(c("#4a6fe3", "white", "#d33f6a"))(100),  #c("blue", "white", "red"))(100)
                     p.mat = cor_pvals,
                     sig.level = 0.05,
                     insig="blank",
                     mar = c(0, 0, 1.75, 0)
                     )$corrPos -> p1
  #text(p1$x, p1$y, round(p1$corr, 2))
  
  # Draw a rectangle around the entire correlation matrix
  rect(0.5, 0.5, ncol(cormatrix) + 0.5, nrow(cormatrix) + 0.5, border = "black", lwd = 2)
  dev.off()
}


# Bayesian corplot: Function to compute a matrix of Bayes Factors for all pairwise correlations
bayes_factor_matrix <- function(data, bayes_factor, savepath) { # , rscale = "medium" - medium is default for width of prior
  # make empty matrix to fill
  bayes_matrix <- matrix(NA, nrow = ncol(data), ncol = ncol(data))
  colnames(bayes_matrix) <- colnames(data)
  rownames(bayes_matrix) <- colnames(data)

  # estimate bayes factors and fill matrix
  for (i in 1:(ncol(data) - 1)) {
    for (j in (i + 1):ncol(data)) {
      
      # first for this correlation data pair remove NAs
      pair_data <- data[, c(i, j)][complete.cases(data[, c(i, j)]), ]
      # estimate bayes factors and fill matrix
      bf <- correlationBF(pair_data[[1]], pair_data[[2]]) #, rscale = rscale
      bf_10 <- extractBF(bf)$bf  # BF10
      if (bayes_factor == 'alternative') {
        bayes_matrix[i, j] <- as.numeric(bf_10)
        bayes_matrix[j, i] <- as.numeric(bf_10) 
      }
      else if (bayes_factor == 'null') {
        bf_01     <- 1 / bf_10 # BF01 
        bayes_matrix[i, j] <- bf_01
        bayes_matrix[j, i] <- bf_01
      }
    }
  }
  diag(bayes_matrix) <- NA # Diagonal is not applicable
  # Mask the lower triangle
  #bayes_matrix[lower.tri(bayes_matrix)] <- NA

  colourpalette <- colorRampPalette(brewer.pal(9, "PuBu"))
  
  cp1 <- ggcorrplot(bayes_matrix, hc.order = FALSE, method = "square", 
  #lab= TRUE, # labels
  #lab_size = 1,
  #digits = 2,
  type = 'lower',
  outline.col = "black",
  ggtheme = ggplot2::theme_minimal,
  tl.cex = 6,
  ) +
  scale_fill_gradientn(
    colors = c("#f3e8ff", colourpalette(100)),
    #colors = colourpalette <- colourpalette(100),
    values = scales::rescale(c(0, 1, max(bayes_matrix, na.rm = TRUE))),
    #limits = c(0, max(bayes_matrix+1, na.rm = TRUE)), 
    name = "Bayes Factor 01",
    na.value = "lightgrey"  # Set a custom color for NA values
  ) +
  scale_y_discrete(position='right') +
  theme(
  plot.title = element_blank(),        # Remove the main title
  plot.subtitle = element_blank(),     # Remove subtitle
  axis.title.x = element_blank(),      # Remove x-axis title
  axis.title.y = element_blank(),      # Remove y-axis title
  panel.grid.major = element_blank(),  # Remove major grid lines
  panel.grid.minor = element_blank(),   # Remove minor grid lines
  plot.margin = unit(c(2, 2, 2, 2), "cm"),
  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 6), #
  axis.text.y = element_text(size = 6)
  )
  
  png(filename = savepath, res = 300, units = "cm", width = 16, height = 15) 
  print(cp1)
  dev.off()
  #return(bayes_matrix)
}


scatterplot_gg <- function(cdat, yvar, xvar, colour) {
  
  corrdata <- data.frame(apply(cdat, 2, rank))
  pval_fdr <- psych::corr.test(cdat, method = "spearman", adjust = "fdr")$p
  rval_fdr <- psych::corr.test(cdat, method = "spearman", adjust = "fdr")$r

    if (pval_fdr[xvar,yvar] < 0.001) {
      pval = '<.001'
    } else {
      pval = round(pval_fdr[xvar,yvar], 3)
    }
  
  # Remove rows with missing values in xvar or yvar before plotting
  cdat <- cdat[!is.na(cdat[[xvar]]) & !is.na(cdat[[yvar]]), ]

  ggplot(cdat, aes(y= !! sym(yvar), x= !! sym(xvar))) + 
    geom_point(color=colour, alpha=0.5, size = 3) +
    geom_smooth(method=lm , color="#909086", fill="#5d9fcc" , se=TRUE) +
    theme_classic() +
    ggtitle(paste("rs =", round(rval_fdr[xvar,yvar], 3), ", pFDR =", pval))+ 
    theme(plot.title = element_text(size = 19, face = "bold"), 
          axis.title = element_text(size = 20), 
          axis.text = element_text(size = 20),
          axis.title.x = element_text(margin = margin(t = 10)), # Add space above x-axis label
          axis.title.y = element_text(margin = margin(r = 10))  # Add space to the right of y-axis label)
    )
}

# partial correlation function
cormatrix_partial <- function(cordata, covariates, title, subtitle, savepath) {
  # Identify the variables of interest
  vars_of_interest <- setdiff(names(cordata), covariates)
  
  # Initialize matrices for correlations and p-values
  n_vars <- length(vars_of_interest)
  r_matrix <- matrix(NA, n_vars, n_vars, dimnames = list(vars_of_interest, vars_of_interest))
  p_matrix <- matrix(NA, n_vars, n_vars, dimnames = list(vars_of_interest, vars_of_interest))
  
  # Loop through variable pairs to compute pairwise correlations and p-values
  for (i in seq_along(vars_of_interest)) {
    for (j in seq_along(vars_of_interest)) {
      if (i != j) {
        # Subset data for the two variables and covariates
        pair_data <- cordata[, c(vars_of_interest[i], vars_of_interest[j], covariates)]
        pair_data <- pair_data[complete.cases(pair_data), ] # remove missing data for this pair
        
        # Ensure enough rows for computation
        if (nrow(pair_data) > length(covariates) + 2) {
          # Compute partial correlation
          result <- pcor.test(pair_data[ ,vars_of_interest[i]], pair_data[ ,vars_of_interest[j]], pair_data[ ,covariates], method = "spearman")
          r_matrix[i, j] <- result$estimate
          p_matrix[i, j] <- result$p.value
          
        }
      }
    }
  }
  
  # FDR correct - explicit safe order version
  p_matrix_fdr <- matrix(NA, nrow(p_matrix), ncol(p_matrix), 
                          dimnames = dimnames(p_matrix))
  
  upper_idx <- which(upper.tri(p_matrix), arr.ind = TRUE)
  fdr_p_vals <- p.adjust(p_matrix[upper_idx], method = "BH")
  
  for (k in seq_len(nrow(upper_idx))) {
    i <- upper_idx[k, 1]
    j <- upper_idx[k, 2]
    p_matrix_fdr[i, j] <- fdr_p_vals[k]
    p_matrix_fdr[j, i] <- fdr_p_vals[k]  # mirror explicitly
  }
  # Then use p_matrix_fdr in the plot
  cp1 <- ggcorrplot(r_matrix, p.mat = p_matrix_fdr, hc.order = FALSE,
                    type = 'lower', insig = 'blank', method = "square", 
                    sig.level = 0.05, outline.col = "black",
                    ggtheme = ggplot2::theme_minimal(),
                    tl.cex = 8,
                    colors = c("#4a6fe3", "white", "#d33f6a")) + #c("#6D9EC1", "white", "#EA5F21FF")) +
    geom_hline(yintercept = n_vars + 0.5, linetype = 3, size = 1) +
    geom_vline(xintercept = 0.5, linetype = 3, size = 1) +
    geom_abline(intercept = 0, slope = 1, linetype = 3, size = 1) +
    ggtitle(title) +
    labs(subtitle = subtitle) +
    theme(
      axis.text.x = element_markdown(),
      axis.text.y = element_markdown()
    )
  
  # Save the plot
  png(filename = savepath, res = 300, units = "cm", width = 15, height = 15) 
  print(cp1)
  dev.off()
  
  # Return correlation and p-value matrices
  return(list(cor_matrix = r_matrix, p_matrix = p_matrix, p_matrix_fdr = p_matrix_fdr))
}

```


# MAIA x Intero-task Correlations & Null Bayes Factors
```{r}

# Just MAIA - with hierarchical intero
colnames(alldata) <- gsub("_", ".", colnames(alldata)) # change _ to . in colnames
cols = c("RRST.conf", "RRST.slope", "RRST.thresh", "mratio.rrst", "HRD.conf", "HRD.slope", "HRD.absthresh", "mratio.hrd", 'maia.notice', 'maia.ndistract', 'maia.nworry', 'maia.attnReg', 'maia.EmoAware', 'maia.SelfRef', 'maia.listen', 'maia.trust')
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("RRST Conf", "RRST Slope", "RRST Thresh", "RRST MRatio", "HRDT Conf", "HRDT Slope", "HRDT Thresh", "HRDT MRatio", 'MAIA Notice', 'MAIA NotDistract', 'MAIA NotWorry', 'MAIA AttenReg', 'MAIA EmotAware', 'MAIA SelfReg', 'MAIA Listen', 'MAIA Trust')
cormatrix_full(corrdata, "MAIA", "Intero & MAIA Correlations", "~/Git/InteroMentalHealth/figures/Intero_correlations/corr_MAIA_Intero_full_.png")
cormatrix_selected(corrdata, "Intero", "Psych", 8, 8, "~/Git/InteroMentalHealth/figures/Intero_correlations/corr_MAIA_Intero.png")
bayes_factor_matrix(corrdata, 'null', "~/Git/InteroMentalHealth/figures/Intero_correlations/Bayes_01/Bayes01corr_MAIA_Intero.png")


pval_fdr <- round(psych::corr.test(corrdata, method = "spearman", adjust = "fdr")$p,3)
rval_fdr <- round(psych::corr.test(corrdata, method = "spearman", adjust = "fdr")$r, 3)


```


# Psych x Intero/MAIA correlations & Null Bayes Factors
```{r}

# Select ALL levels of Multi Psych EFA factors with hierarchical intero
cols = c("RRST.conf", "RRST.slope", "RRST.thresh", "mratio.rrst", "HRD.conf", "HRD.slope", "HRD.absthresh", "mratio.hrd", "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("RRST Conf", "RRST Slope", "RRST Thresh", "RRST MRatio", "HRDT Conf", "HRDT Slope", "HRDT Thresh", "HRDT MRatio", "<b>Affective Symptoms</b>", "<b>ADHD & Somatic</b>", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")
cormatrix_full(corrdata, "Multi-level Psych EFA", "Intero & Psych Correlations", "~/Git/InteroMentalHealth/figures/Intero_correlations/corr_multiEFAFULL_Intero_full_.png")
cormatrix_selected(corrdata, "Intero", "Psych", 8, 11, "~/Git/InteroMentalHealth/figures/Intero_correlations/corr_multiEFAFULL_Intero.png")
bayes_factor_matrix(corrdata, 'null', "~/Git/InteroMentalHealth/figures/Intero_correlations/Bayes_01/Bayes01corr_multiEFAFULL_Intero_.png")


# Select  ALL levels of Multi Psych EFA factors with MAIA
cols = c('maia.notice', 'maia.ndistract', 'maia.nworry', 'maia.attnReg', 'maia.EmoAware', 'maia.SelfRef', 'maia.listen', 'maia.trust',  "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c('MAIA Notice', 'MAIA NotDistract', 'MAIA NotWorry', 'MAIA AttenReg', 'MAIA EmotAware', 'MAIA SelfReg', 'MAIA Listen', 'MAIA Trust', "<b>Affective Symptoms</b>", "<b>ADHD & Somatic</b>", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")
cormatrix_full(corrdata, "Multi-level Psych EFA", "MAIA & Psych Correlations", "~/Git/InteroMentalHealth/figures/Intero_correlations/corr_multiEFAFULL_MAIA_full_.png")
cormatrix_selected(corrdata, "Intero", "Psych", 8, 11, "~/Git/InteroMentalHealth/figures/Intero_correlations/corr_multiEFAFULL_MAIA.png")
bayes_factor_matrix(corrdata, 'null', "~/Git/InteroMentalHealth/figures/Intero_correlations/Bayes_01/MAIA/Bayes01corr_multiEFAFULL_MAIA.png")

#pval_fdr <- round(psych::corr.test(corrdata, method = "spearman", adjust = "fdr")$p,3)
#rval_fdr <- round(psych::corr.test(corrdata, method = "spearman", adjust = "fdr")$r, 3)

# cor_result <- psych::corr.test(corrdata, method = "spearman", adjust = "fdr", ci = TRUE)
# var1 <- "RRST Slope"
# var2 <- "<b>Affective Symptoms</b>"
# ci_row <- "HRDTT-Autsm"
# 
# cat(sprintf(
#   "%s & %s: rs (%d) = %.3f, pFDR = %.3f\n, 95%% CI's = %.3f, %.3f",
#   var1, var2,
#   cor_result$n[var1, var2] - 2,
#   cor_result$r[var1, var2],
#   cor_result$p[var1, var2],
#   cor_result$ci[ci_row, "lower"],
#   cor_result$ci[ci_row, "upper"]
# ))
# 
# format(cor_result$p[var1, var2], scientific = FALSE)

```


# MAIA (mean score) figures
```{r}
# Select overall MAIA score with all mental health 
cols = c("maia.full.mean", "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("MAIA Mean", "<b>Affective Symptoms</b>", "<b>ADHD & Somatic</b>", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")
cormatrix_full(corrdata, "Multi Level Psych EFA", "MAIA & Psych Correlations", "~/Git/InteroMentalHealth/figures/Intero_correlations/MAIA/corr_multiEFA_MAIAmean_full.png")
cormatrix_selected(corrdata, "Intero", "Psych", 8, 2, "~/Git/InteroMentalHealth/figures/Intero_correlations/MAIA/corr_multiEFA_MAIAmean.png")
bayes_factor_matrix(corrdata, 'null', "~/Git/InteroMentalHealth/figures/Intero_correlations/Bayes_01/MAIA/Bayes01corr_multiEFA_MAIAmean_text.png")

# # scatterplots 
p1 = scatterplot_gg(corrdata, 'Affective Symptoms', 'MAIA Mean', "#177ab4")
p1
ggsave("~/Git/InteroMentalHealth/figures/Intero_correlations/scatter_NMH_MAIA_blue.png", height = 8, width = 6, dpi = 300, units = "in")

# colnames(corrdata) <- c('MAIA Notice', 'MAIA NotDistract', 'MAIA NotWorry', 'MAIA AttenReg', 'MAIA EmotAware', 'MAIA SelfReg', 'MAIA Listen', 'MAIA Trust', "Affective Symptoms", "ADHD & Somatic", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")
# p2 = scatterplot_gg(corrdata, 'Affective Symptoms', 'MAIA Trust', "#177ab4")
# p2
# ggsave("~/Git/InteroMentalHealth/figures/Intero_correlations/scatter_NMH_MAIATrusting.png", height = 8, width = 5, dpi = 300, units = "in")

```


# HRD extero corr with Psych multiEFA & maia
```{r}

# Select HRDextero & ALL levels of Multi Psych EFA factors & MAIA
cols = c("HRDextero.conf", "HRDextero.slope", "HRDextero.absthresh", "mratio.extero", 'maia.notice', 'maia.ndistract', 'maia.nworry', 'maia.attnReg', 'maia.EmoAware', 'maia.SelfRef', 'maia.listen', 'maia.trust',  "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("HRDTextero Conf", "HRDTextero Slope", "HRDTextero Thresh", "HRDTextero MRatio", 'MAIA Notice', 'MAIA NotDistract', 'MAIA NotWorry', 'MAIA AttenReg', 'MAIA EmotAware', 'MAIA SelfReg', 'MAIA Listen', 'MAIA Trust', "<b>Affective Symptoms</b>", "<b>ADHD & Somatic</b>", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")
cormatrix_full(corrdata, "HRD Extero Correlations", "HRD Extero, MAIA, & Multi-level Psych EFA ", "~/Git/InteroMentalHealth/figures/Extero_correlations/corr_HRDextero_multiEFAFULL_MAIA_full_.png")
cormatrix_selected(corrdata, "Extero", "Maia & Psych", 4, 19, "~/Git/InteroMentalHealth/figures/Extero_correlations/corr_HRDextero_multiEFAFULL_MAIA.png")
bayes_factor_matrix(corrdata, 'null', "~/Git/InteroMentalHealth/figures/Extero_correlations/Bayes01corr_HRDextero_multiEFAFULL_MAIA_.png")

```


# Partial correlation matrices controlling for age, gender, bmi
```{r}
library(ggtext)
        
# Select ALL levels of Multi Psych EFA factors with hierarchical intero
cols = c("age", "gender", "bmi", "RRST.conf", "RRST.slope", "RRST.thresh", "mratio.rrst", "HRD.conf", "HRD.slope", "HRD.absthresh", "mratio.hrd", "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("Age", "Gender", "BMI", "RRST Conf", "RRST Slope", "RRST Thresh", "RRST MRatio", "HRDT Conf", "HRDT Slope", "HRDT Thresh", "HRDT MRatio", "Affective Symptoms", "ADHD & Somatic", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")

# Run the function
partialresults <- cormatrix_partial(
  cordata = corrdata, 
  covariates = c("Age", "Gender", "BMI"), 
  title = "Partial Correlation Matrix", 
  subtitle = "Controlling for Age, Gender, and BMI", 
  savepath = "~/Git/InteroMentalHealth/figures/Intero_correlations/partial_corr/partialcorr_multiEFAFULL_Intero_fdr.png"
)




# Select  ALL levels of Multi Psych EFA factors with MAIA
cols = c("age", "gender", "bmi", 'maia.notice', 'maia.ndistract', 'maia.nworry', 'maia.attnReg', 'maia.EmoAware', 'maia.SelfRef', 'maia.listen', 'maia.trust',  "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("Age", "Gender", "BMI", 'MAIA Notice', 'MAIA NotDistract', 'MAIA NotWorry', 'MAIA AttenReg', 'MAIA EmotAware', 'MAIA SelfReg', 'MAIA Listen', 'MAIA Trust', "Affective Symptoms", "ADHD & Somatic", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")

# Run the function
partialresults <- cormatrix_partial(
  cordata = corrdata, 
  covariates = c("Age", "Gender", "BMI"), 
  title = "Partial Correlation Matrix", 
  subtitle = "Controlling for Age, Gender, and BMI", 
  savepath = "~/Git/InteroMentalHealth/figures/Intero_correlations/partial_corr/partialcorr_multiEFAFULL_MAIA_fdr.png"
)


# Select HRDextero & ALL levels of Multi Psych EFA factors & MAIA
cols = c("age", "gender", "bmi", "HRDextero.conf", "HRDextero.slope", "HRDextero.absthresh", 'mratio.extero', 'maia.notice', 'maia.ndistract', 'maia.nworry', 'maia.attnReg', 'maia.EmoAware', 'maia.SelfRef', 'maia.listen', 'maia.trust',  "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("Age", "Gender", "BMI", "HRDTextero Conf", "HRDTextero Slope", "HRDTextero Thresh", 'HRDTextero MRatio', 'MAIA Notice', 'MAIA NotDistract', 'MAIA NotWorry', 'MAIA AttenReg', 'MAIA EmotAware', 'MAIA SelfReg', 'MAIA Listen', 'MAIA Trust', "Affective Symptoms", "ADHD & Somatic", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")

# Run the function
partialresults <- cormatrix_partial(
  cordata = corrdata, 
  covariates = c("Age", "Gender", "BMI"), 
  title = "Partial Correlation Matrix", 
  subtitle = "Controlling for Age, Gender, and BMI", 
  savepath = "~/Git/InteroMentalHealth/figures/Intero_correlations/partial_corr/partialcorr_HRDextero_multiEFAFULL_MAIA_fdr.png"
)



# Just MAIA - with hierarchical intero
colnames(alldata) <- gsub("_", ".", colnames(alldata)) # change _ to . in colnames
cols = c("age", "gender", "bmi", "RRST.conf", "RRST.slope", "RRST.thresh", "mratio.rrst", "HRD.conf", "HRD.slope", "HRD.absthresh", "mratio.hrd", 'maia.notice', 'maia.ndistract', 'maia.nworry', 'maia.attnReg', 'maia.EmoAware', 'maia.SelfRef', 'maia.listen', 'maia.trust')
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("Age", "Gender", "BMI", "RRST Conf", "RRST Slope", "RRST Thresh", "RRST MRatio", "HRDT Conf", "HRDT Slope", "HRDT Thresh", "HRDT MRatio", 'MAIA Notice', 'MAIA NotDistract', 'MAIA NotWorry', 'MAIA AttenReg', 'MAIA EmotAware', 'MAIA SelfReg', 'MAIA Listen', 'MAIA Trust')

# Run the function
partialresults <- cormatrix_partial(
  cordata = corrdata, 
  covariates = c("Age", "Gender", "BMI"), 
  title = "Partial Correlation Matrix", 
  subtitle = "Controlling for Age, Gender, and BMI", 
  savepath = "~/Git/InteroMentalHealth/figures/Intero_correlations/partial_corr/partialcorr_MAIA_Intero_fdr.png"
)

```

   
# Demographics
```{r}
#alldata <- read.csv("~/Git/InteroMentalHealth/data/alldata.csv")
# "RRST_conf", "RRST_slope", "RRST_thresh", "HRD_conf", "HRD_slope", "HRD_absthresh")
cols = c("age", "gender",  "HRD.conf", "HRD.slope", "HRD.absthresh") #,"mratio.hrd","RRST.conf","RRST.slope","RRST.thresh""mratio.rrst") 
demodata <- alldata[ ,cols] 
N = colSums(!is.na(demodata))
demodata <- demodata[complete.cases(demodata), ]

# age
min_age = min(demodata$age)
max_age = max(demodata$age)
median_age = median(demodata$age)
#gender
Nfemales = sum(demodata$gender == 1)   
Nmales = sum(demodata$gender == 2)   
Nother = sum(demodata$gender == 3)  

```


# Descriptive Tables
```{r}
# Save Descriptives Table 
library(flextable)

cols = c("RRST.conf", "RRST.slope", "RRST.thresh", "mratio.rrst", "HRD.conf", "HRD.slope", "HRD.absthresh", "mratio.hrd", "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
int_data <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(int_data) <- c("RRST Conf", "RRST Slope", "RRST Thresh", "RRST MRatio", "HRDT Conf", "HRDT Slope", "HRDT Thresh", "HRDT MRatio", "<b>Affective Symptoms</b>", "<b>ADHD & Somatic</b>", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")

desc_stats <- data.frame(
  Variable = colnames(int_data),
  N = colSums(!is.na(int_data)),
  Mean = round(colMeans(int_data, na.rm = TRUE), 3),
  SD = round(apply(int_data, 2, sd, na.rm = TRUE), 3),
  #Median = round(apply(int_data, 2, median, na.rm = TRUE), 3),
  #Range = apply(int_data, 2, function(x) paste0(round(min(x, na.rm = TRUE), 3), " - ", round(max(x, na.rm = TRUE), 3))),
  CI_95 = apply(int_data, 2, function(x) {
    x <- na.omit(x)
    ci <- t.test(x)$conf.int  # Compute 95% CI
    paste0(round(ci[1], 3), ", ", round(ci[2], 3))
  })
)

# Format the table in APA style
apa_table <- flextable(desc_stats) %>%
  set_header_labels(Variable = "Variable", Mean = "Mean", SD = "Standard Deviation", CI_95 = "95% CI") %>%
  autofit()


# Print the table
apa_table
save_as_docx(apa_table, path = "~/Git/InteroMentalHealth/tables/APA_Descriptives.docx")


# Save Descriptives Table  MAIA
cols = c('maia.notice', 'maia.ndistract', 'maia.nworry', 'maia.attnReg', 'maia.EmoAware', 'maia.SelfRef', 'maia.listen', 'maia.trust')
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c('MAIA Notice', 'MAIA NDistract', 'MAIA NWorry', 'MAIA AttnReg', 'MAIA EmoAware', 'MAIA SelfRef', 'MAIA Listen', 'MAIA Trust')
desc_stats <- data.frame(
  Variable = colnames(corrdata),
  N = colSums(!is.na(corrdata)), 
  Mean = round(colMeans(corrdata, na.rm = TRUE), 3),
  SD = round(apply(corrdata, 2, sd, na.rm = TRUE), 3),
  #Median = round(apply(corrdata, 2, median, na.rm = TRUE), 3),
  #Range = apply(corrdata, 2, function(x) paste0(round(min(x, na.rm = TRUE), 3), " - ", round(max(x, na.rm = TRUE), 3)))
  CI_95 = apply(corrdata, 2, function(x) {
  x <- na.omit(x)
  ci <- t.test(x)$conf.int  # Compute 95% CI
  paste0(round(ci[1], 3), ", ", round(ci[2], 3))
  })
)
# Format the table in APA style
apa_table <- flextable(desc_stats) %>%
  set_header_labels(Variable = "Variable", Mean = "Mean", SD = "Standard Deviation") %>%
  autofit()
# Print the table
apa_table
save_as_docx(apa_table, path = "~/Git/InteroMentalHealth/tables/APA_Descriptives_MAIA.docx")

```


# Null scatterplots of intero & mental health
```{r}
cols = c("RRST.conf", "RRST.slope", "RRST.thresh", "mratio.rrst", "HRD.conf", "HRD.slope", "HRD.absthresh", "mratio.hrd", "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
int_data <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(int_data) <- c("RRST Conf", "RRST Slope", "RRST Thresh", "RRST MRatio", "HRDT Conf", "HRDT Slope", "HRDT Abs Thresh", "HRDT MRatio", "Affective Symptoms", "ADHD & Somatic", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")

library(ggplot2)
library(ggExtra)
library(BayesFactor)
library(psych)
library(ggpubr)


plot_scatter <- function(df, x, y) {
  df_complete <- df[complete.cases(df[[x]], df[[y]]), ]
  fit <- lm(df_complete[[y]] ~ df_complete[[x]])
  preds <- predict(fit, interval = "prediction")
  df_complete$fit <- preds[, "fit"]
  df_complete$lwr <- preds[, "lwr"]
  df_complete$upr <- preds[, "upr"]

  cor_result <- psych::corr.test(df_complete[, c(x, y)], method = "spearman", adjust = "fdr", ci = TRUE)
  r <- cor_result$r[1, 2]
  ci_lower <- cor_result$ci[1, "lower"]
  ci_upper <- cor_result$ci[1, "upper"]
  p_fdr <- cor_result$p[1, 2]

  bf <- BayesFactor::correlationBF(df_complete[[x]], df_complete[[y]])
  bf_10 <- exp(bf@bayesFactor$bf)
  bf_01 <- round(1 / bf_10, 2)

  stat_label <- sprintf("rs = %.2f [%.2f, %.2f], pFDR = %.3f, BF₀₁ = %.2f", r, ci_lower, ci_upper, p_fdr, bf_01)

  p <- ggplot(df_complete, aes(x = .data[[x]], y = .data[[y]])) +
    geom_point(shape = 21, fill = "#4D9CF5", color = "grey40", size = 2.5, alpha = 0.6) +
    geom_smooth(method = "lm", se = TRUE, level = 0.95,
                color = "#6C74DD", fill = "#C5C7EC", linewidth = 1.1) +
    geom_line(aes(y = lwr), linetype = "dashed", color = "grey50", linewidth = 0.6) +
    geom_line(aes(y = upr), linetype = "dashed", color = "grey50", linewidth = 0.6) +
    theme_minimal(base_size = 13) +
    theme(
      axis.title.x = element_text(size = 17, margin = margin(t = 5)),
      axis.title.y = element_text(size = 17, margin = margin(r = 5)),
      axis.text = element_text(size = 16),
      plot.margin = margin(t = 20, r = 5, b = 60, l = 5),
      panel.background = element_rect(fill = "white", color = NA),
      plot.background = element_rect(fill = "white", color = NA),
      plot.caption = element_text(size = 13, hjust = 0.5, color = "grey20", margin = margin(t = 10))
    ) +
    labs(x = x, y = y, caption = stat_label)

  ggMarginal(p, type = "histogram", fill = "#C5C7EC", color = "grey60", bins = 20)
}


# Plots
#p1 <- plot_scatter(int_data, "Negative Mental Health", "Anxiety & ADHD") # "Mental Health Grand Factors"
p2 <- plot_scatter(int_data, "Affective Symptoms", "HRDT Abs Thresh")
p3 <- plot_scatter(int_data, "Affective Symptoms", "HRDT Slope")
p4 <- plot_scatter(int_data, "Affective Symptoms", "RRST Thresh")
p5 <- plot_scatter(int_data, "Affective Symptoms", "RRST Slope")
p6 <- plot_scatter(int_data, "ADHD & Somatic", "HRDT Abs Thresh")
p7 <- plot_scatter(int_data, "ADHD & Somatic", "HRDT Slope")
p8 <- plot_scatter(int_data, "ADHD & Somatic", "RRST Thresh")
p9 <- plot_scatter(int_data, "ADHD & Somatic", "RRST Slope")

# Arrange them together
combined <- ggarrange(p2, p4, p6, p8, ncol = 2, nrow = 2) #  p3, p5, p7, p9,

# Save to file
ggsave("~/Git/InteroMentalHealth/figures/Intero_correlations/MHintero_scatter__.png", combined, width = 12, height = 13, dpi = 300, bg = "white")

```

# Psych sum score correlations
```{r}
cols = c("RRST.conf", "RRST.slope", "RRST.thresh", "mratio.rrst", "HRD.conf", "HRD.slope", "HRD.absthresh", "mratio.hrd", 'maia.notice', 'maia.ndistract', 'maia.nworry', 'maia.attnReg', 'maia.EmoAware', 'maia.SelfRef', 'maia.listen', 'maia.trust', 'aq10', 'asrs.a.sum', 'asrs.b.sum', 'mdi', 'phq9', 'phq15', 'pss', 'sias', 'stai.trait')
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("RRST Conf", "RRST Slope", "RRST Thresh", "RRST MRatio", "HRDT Conf", "HRDT Slope", "HRDT Thresh", "HRDT MRatio", 'MAIA Notice', 'MAIA NotDistract', 'MAIA NotWorry', 'MAIA AttenReg', 'MAIA EmotAware', 'MAIA SelfReg', 'MAIA Listen', 'MAIA Trust', 'AQ10', 'ASRS.A', 'ASRS.B', 'MDI', 'PHQ9', 'PHQ15', 'PSS', 'SIAS', 'STAI.trait') #"asrs_combined_sum"
cormatrix_full(corrdata, "Psych Sum Scores", "Intero & Psych Correlations", "~/Git/InteroMentalHealth/figures/Intero_correlations/Psychsumscores_correlations/corr_Psychsumscores_Intero_full.png")
cormatrix_selected(corrdata, "Intero", "Psych", 16, 8, "~/Git/InteroMentalHealth/figures/Intero_correlations/Psychsumscores_correlations/corr_Psychsumscores_Intero.png")
bayes_factor_matrix(corrdata, 'null', "~/Git/InteroMentalHealth/figures/Intero_correlations/Psychsumscores_correlations/Bayes01corr_Psychsumscores_Intero_.png")

```


# Check if multiple comparisons correction was too conservation
```{r}
colnames(corrdata) <- c("RRST Conf", "RRST Slope", "RRST Thresh", "RRST MRatio", "HRDT Conf", "HRDT Slope", "HRDT Thresh", "HRDT MRatio", "Affective Symptoms", "ADHD & Somatic", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")

# First uncorrected (selecting only the inter-mentalhealth comparisons of interest)
ct_uncorr <- psych::corr.test(corrdata, method = "spearman", adjust = "none")
r <- ct_uncorr$r
p <- ct_uncorr$p
sig_intero_psych <- r[1:8, 9:21][ p[1:8, 9:21] < 0.05 ]

summary(sig_intero_psych)
summary(abs(sig_intero_psych))
range(sig_intero_psych, na.rm = TRUE)

# FDR correct only those (i.e., not including mentalhealth with itself)
ct <- psych::corr.test(corrdata, method = "spearman", adjust = "none")
r <- ct$r[1:8, 9:21]
p <- ct$p[1:8, 9:21]

p_fdr <- p.adjust(p, method = "fdr")

summary(r[p_fdr < 0.05])
summary(abs(r[p_fdr < 0.05]))
range(r[p_fdr < 0.05], na.rm = TRUE)


ggcorrplot(r, hc.order = FALSE, p.mat = p_fdr,
           type = "full", method = "square",
           insig = "blank", sig.level = 0.05,
           outline.col = "black",
           ggtheme = ggplot2::theme_minimal,
           tl.cex = 8,
           colors = c("#4a6fe3", "white", "#d33f6a")) +
  ggtitle("Intero × Mental Health (FDR within test family)") +
  theme(
    axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1),
    axis.text.y = ggtext::element_markdown()
  )

# effect size:
summary(abs(sig_intero_psych))
range(sig_intero_psych, na.rm = TRUE)

# CIs
library(psych)
ci <- psych::r.con(r = sig_intero_psych, n = nrow(corrdata))
summary(ci)


# Bayes
library(BayesFactor)
idx_intero <- 1:8
idx_mh <- 9:21

bf10_num <- function(x, y) {
  d <- na.omit(data.frame(x = x, y = y))
  if (nrow(d) < 10) return(NA_real_)
  bf_obj <- correlationBF(rank(d$x), rank(d$y))
  extractBF(bf_obj, onlybf = TRUE)  # <- numeric BF10
}

BF10 <- as.vector(
  outer(idx_intero, idx_mh,
        Vectorize(function(i, j)
          bf10_num(corrdata[[i]], corrdata[[j]])))
)
BF01 <- 1 / BF10

summary(BF01)
mean(BF01 > 1, na.rm = TRUE)
mean(BF01 > 3, na.rm = TRUE)
range(BF01, na.rm = TRUE)


```

# Task Accuracy correlations
```{r}

# Select ALL levels of Multi Psych EFA factors with hierarchical intero
cols = c("RRST.accuracy", "HRD.accuracy", "HRDextero.accuracy", "multiEFA.l2.Negative Mental Health", "multiEFA.l2.Anxiety & ADHD", "multiEFA.l1.Social Anxiety", "multiEFA.l1.Happiness/Self-Esteem", "multiEFA.l1.Insomnia/Fatigue", "multiEFA.l1.Inattentiveness", "multiEFA.l1.Depression", "multiEFA.l1.Anxiety", "multiEFA.l1.Restlessness", "multiEFA.l1.Stress", "multiEFA.l1.Autism", "multiEFA.l1.Somatic", "multiEFA.l1.Impulsivity")
corrdata <- alldata[ ,cols]#[complete.cases(alldata[, cols]),] # select cols 
colnames(corrdata) <- c("RRST Accuracy", "HRDT Accuracy", "Extero Accuracy", "Affective Symptoms", "ADHD & Somatic", "Social Anxiety", "Self-Confidence", "Sleep", "Inattentiveness", "Depression", "Negative Thoughts", "Restlessness", "Stress", "Autism", "Somatic", "Impulsivity")
cormatrix_full(corrdata, "Multi-level Psych EFA", "Accuracy & Psych Correlations", "~/Git/InteroMentalHealth/figures/Intero_correlations/corr_multiEFAFULL_InteroAccuracy.png")
bayes_factor_matrix(corrdata, 'null', "~/Git/InteroMentalHealth/figures/Intero_correlations/Bayes_01/Bayes01corr_multiEFAFULL_InteroAccuracy.png")

```


